Spatiotemporal model of `r paste(params$species)` biomass

### 2020-11-28 analysis/sand-lance/biomass-density-model.Rmd
make sandy linear only in sand lance density model

---
title: "Spatiotemporal model of `r paste(params$species)` biomass"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Pacific Sand Lance"
    region: "Non-HG surveys"
    knots: 400
    # covs: "-sand-depth-roms"
    # covs: "-depth-roms"
    # covs: "-sand-depth-temp"
    # covs: "-mud-depth-temp"
    # covs: "-mud-sand-depth-temp"
    covs: "-sand-x-depth-temp" # doesn't converge
    REML: FALSE
    AR1: TRUE
    fixed_spatial: TRUE
    update_model: TRUE
    # update_model: FALSE
    update_model_check: TRUE
    update_predictions: TRUE
---

@@

if(params$covs == "-sand-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(sandy_scaled, k = 3) + 
  s(sandy_scaled, by = shallow, k = 3) + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-mud-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  s(muddy_scaled, k = 2) + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

@@

```{r}
g1 <- ggplot(pred,
      aes(density, exp(est), colour = as.factor(ssid))) +
    geom_abline(slope=1, intercept = 0) +
    scale_x_continuous(trans = 'log10') +
    scale_y_continuous(trans = 'log10') +
    geom_point(alpha = 0.2) 
g1
```

@@

```{r}
if(covs %in% c("-sand-depth-roms", "-sand-depth-temp", "-mud-sand-depth-temp")){
nd_sand <- data.frame(
  depth_scaled = min(data$depth_scaled), 
  shallow = 1,
  sandy_scaled = seq(min(data$sandy_scaled), 
    max(data$sandy_scaled), length.out = 50),
  muddy_scaled = min(data$muddy_scaled),
  roms_scaled = 0,
  temp_scaled = 0,
  year_pair = 2011 # a chosen year
)

>>>>

---
title: "Spatiotemporal model of `r paste(params$species)` biomass"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Pacific Sand Lance"
    region: "Non-HG surveys"
    knots: 400
    # covs: "-sand-depth-roms"
    # covs: "-depth-roms"
    # covs: "-sand-depth-temp"
    covs: "-mud-depth-temp"
    # covs: "-mud-sand-depth-temp"
    # covs: "-sand-shallow-depth-temp"
    # covs: "-sand-x-depth-temp" # doesn't converge
    REML: FALSE
    AR1: TRUE
    fixed_spatial: TRUE
    # update_model: FALSE
    update_model: TRUE
    update_model_check: TRUE
    update_predictions: TRUE
---

@@

if(params$covs == "-sand-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  sandy_scaled + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

if(params$covs == "-sand-shallow-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  sandy_scaled * shallow + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}
  # s(sandy_scaled, k = 3) + 
  # s(sandy_scaled, by = shallow, k = 3) +

if(params$covs == "-mud-depth-temp"){
mod.formula <- as.formula(paste0(
  "density ~ 0 + as.factor(year_pair) + 
  muddy_scaled + 
  s(depth_scaled, k = 3) + 
  s(temp_scaled, k = 3)"
  ))
clim_cov <- "temp"
}

@@

```{r}
g1 <- ggplot(pred,
      aes(density+0.01, exp(est), colour = as.factor(ssid))) +
    geom_abline(slope=1, intercept = 0) +
    scale_x_continuous(trans = 'log10') +
    scale_y_continuous(trans = 'log10') +
    geom_point(alpha = 0.2) 
g1
```

@@

```{r}
if(covs %in% c("-sand-depth-roms", "-sand-depth-temp", "-mud-sand-depth-temp", "-sand-shallow-depth-temp")){
nd_sand <- data.frame(
  depth_scaled = min(data$depth_scaled), 
  shallow = 1,
  sandy_scaled = seq(min(data$sandy_scaled), 
    max(data$sandy_scaled), length.out = 50),
  muddy_scaled = min(data$muddy_scaled),
  roms_scaled = 0,
  temp_scaled = 0,
  year_pair = 2011 # a chosen year
)
